Near and Mid-infrared properties of known $z\geq5$ Quasars

### 2019-06-10 tex/older_tex/VHzQ_20190610.tex

  \subsubsection{Comparing WFCAM and VISTA}
  There are 130 overlapping QSOs between WFCAM and VISTA. We used the
  {\tt VegaToAB} values to put these objects on the same AB system, and
  for each object compared the two measurements. First, we calculated the
  weighted average (calibrated flux) in each filter of both and
  calculated the ratio and difference between each measurement and the
  average.  Then for each filter we calculated the weighted average of
  the differences (in mag) for each instrument to see if there were
  significant offsets. The results are given in
  Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a significant
  offset is the $Y$-band. All of the VISTA averages are negative and all
  of the WFCAM ones are positive. The $Ks$ versus $K$ band comparison may be
  affected the different shapes of the filters, with $K$ being significantly 
  wider than $K_s$, able to detect light at longer wavelengths.
  \begin{table}
    \centering
    \begin{tabular}{l r r}
      \hline  \hline
      abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
      -  WFCAM)      &                                        &  objects \\
      \hline
      $Z$                 &  23.2 	& 3 \\
      $Y$                 &  57.3 	& 53 \\
      $J$                  &    2.1 	& 106 \\
      $H$                 &  45.8     &  96 \\
      $K_{\rm s}$/$K$ &  25.2     & 110 \\
      \hline  \hline
    \end{tabular}
    \caption{Comparing the magnitudes in different WFCAM/UKIRT and 
      VIRCAM/VISTA near-infrared bands.}
    \label{tab:WFCAM_vs_VISTA}
  \end{table}

  We have also checked for quasars with large differences in magnitude
  between the WSA and VSA. Objects were selected where the average flux
  was $>0.$ and $>5$ average flux error. In order to account for large
  errors in either the WFCAM or VISTA photometry, objects with $\delta$mag$
  < 2 \times$ $\sigma_{\delta\rm mag}$ in either WSA or VSA were removed. This
  selects two quasars with large, $\delta$mag $>0.2$mag differences
  between the WSA and VSA. These are SDSSJ0349+0034 and
  SDSSJ2220-0101. For SDSSJ0349+0034 has a WSA $K$-band magnitude of
  19.13$\pm$0.24, while for the VSA $K_s$-band this is 18.36$\pm$0.10
  mag. For SDSSJ2220-0101, in $J$-band WSA = 22.23$\pm$0.15, for the VSA
  = 19.38$\pm$0.04.

\begin{table}
  \centering
  \begin{tabular}{l r r r r}
    \hline \hline
    \multirow{ 2}{*}{$z \geq$} & \multicolumn{2}{c}{unWISE} &  \multicolumn{2}{c}{ALLWISE}   \\ 
                                             & \multicolumn{1}{c}{W1} & \multicolumn{1}{c}{W2} & \multicolumn{1}{c}{W3} & \multicolumn{1}{c}{W4}  \\ 
    \hline
    5.00   &   362 ( 78.2\%)   &   308 ( 66.5\%)  &    51 ( 11.0\%)  &    10 (  2.2\%) \\ 
    5.70   &   186 ( 69.4\%)   &   151 ( 56.3\%)  &    15 (  5.6\%)  &     2 (  0.7\%) \\ 
    6.00   &   109 ( 63.7\%)   &    91 ( 53.2\%)  &     8 (  4.7\%)  &     2 (  1.2\%) \\ 
    6.19   &    63 ( 72.4\%)   &    47 ( 54.0\%)  &     3 (  3.4\%)  &     2 (  2.3\%) \\ 
    6.50   &    34 ( 85.0\%)   &    26 ( 65.0\%)  &     1 (  2.5\%)  &     2 (  5.0\%) \\ 
    6.78   &    12 ( 85.7\%)   &     9 ( 64.3\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.00   &     4 (100.0\%)   &     4 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.50   &     1 (100.0\%)   &     1 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    \hline \hline
  \end{tabular}
  \caption{Detection rates in the mid-infrared bands from WISE as a function of 
    redshift. A signal-to-noise cut of {\tot w$x$snr}$>3.0$ has been used for each band.}
  \label{tab:WFCAM_vs_VISTA}
\end{table}

@@

\begin{figure}
  %% trim=l b r t
  \includegraphics[width=8.6cm, clip,trim=2mm 0mm 2mm 0mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEsnrW1W2W3W4_2by3_v1.pdf}
  \centering
  \vspace{-14pt}
  \caption[]{WISE signal-to-noise measures for the four bands, as well
    as for (W1-W2) colour.  The points are colour coded by redshift.}
  \label{fig:WISEmag_vs_coverage}
\end{figure}

@@

Recently, \citet{Assef2018} released two large catalogues of AGN 
candidates identified across 30,000 deg$^2$ of extragalactic sky 
from the WISE AllWISE Data Release. The ``R90'' catalogue, 
contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
AGN candidates per deg$^2$) while the ``C75'' catalogue  
consists of 20.9M AGN candidates at 75\% completeness (and 
($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
our catalogue of 463 VH$z$Qs with these catalogues, produces 
42 matches with	the R90 sample and 98 matches with the C75 sample. 
Both catalogues unsurprisingly match to the ultraluminous quasar 
SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
matches to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
matches to J1342+0928 \citep{Banados2018}.

The VH$z$Q with the bluest colour in (W1 - W2) is 
DELS J1048-0109 with (W1-W2) = 0.154 
(see Figure~\ref{fig:DELS_J1048).

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}
    \caption{ (a) UHS J0439+1634 
                 (b) SDSS J0100+2802 
               (c) SDSS J1443+3623 
 (d) SDSS J1623+4705
}
    \label{fig:foobar}
\end{figure*}

@@

\subsection{Variability}
VH$z$Qs, if accreting at, or above the Eddington Limit, might well
have have large values of changing mass accretion rate, $\ddot{m}_{\rm
accr}$. A consequence of this would be that these quasars exhibit signs
of variability, most likely showing up in their UV/optical rest-frame
spectra. We look for evidence of this variability signature in the NIR
and MIR light-curves of the VH$z$Qs. As a guide, \civ enters the
$Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the
$J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the
$H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the
$K$-band at redshift $z=6.25$ and exits at $7.50$.

>>>>

  \subsubsection{Comparing WFCAM and VISTA}
  There are 130 overlapping QSOs between WFCAM and VISTA. We used the
  {\tt VegaToAB} values to put these objects on the same AB system, and
  for each object compared the two measurements. First, we calculated the
  weighted average (calibrated flux) in each filter of both and
  calculated the ratio and difference between each measurement and the
  average.  Then for each filter we calculated the weighted average of
  the differences (in mag) for each instrument to see if there were
  significant offsets. The results are given in
  Table~\ref{tab:WFCAM_vs_VISTA}.  The only filter with a significant
  offset is the $Y$-band. All of the VISTA averages are negative and all
  of the WFCAM ones are positive. The $Ks$ versus $K$ band comparison may be
  affected the different shapes of the filters, with $K$ being significantly wider than $K_s$.
  \begin{table}
    \centering
    \begin{tabular}{l r r}
      \hline  \hline
      abs(VIRCAM & \multirow{2}{*}{millimags} &  no. of  \\
      -  WFCAM)      &                                        &  objects \\
      \hline
      $Z$                 &  23.2 	& 3 \\
      $Y$                 &  57.3 	& 53 \\
      $J$                  &    2.1 	& 106 \\
      $H$                 &  45.8     &  96 \\
      $K_{\rm s}$/$K$ &  25.2     & 110 \\
      \hline  \hline
    \end{tabular}
    \caption{Comparing the magnitudes in different WFCAM/UKIRT and 
      VIRCAM/VISTA near-infrared bands.}
    \label{tab:WFCAM_vs_VISTA}
  \end{table}

  We have also checked for quasars with large differences in magnitude
  between the WSA and VSA. Objects were selected where the average flux
  was $>0.$ and $>5$ average flux error. In order to account for large
  errors in either the WFCAM or VISTA photometry, objects with deltaMag$
  < 2 \times$ deltaMagErr in either WSA or VSA were removed. This
  selects two quasars with large, $\delta$mag $>0.2$mag differences
  between the WSA and VSA. These are SDSSJ0349+0034 and
  SDSSJ2220-0101. For SDSSJ0349+0034 has a WSA $K$-band magnitude of
  19.13$\pm$-0.24, while for the VSA $K_s$-band this is 18.36$\pm$0.10
  mag. For SDSSJ2220-0101, in $J$-band WSA = 22.23$\pm$0.15, for the VSA
  = 19.38$\pm$0.04.

\begin{table}
  \centering
  \begin{tabular}{l r r r r}
    \hline \hline
    \multirow{ 2}{*}{$z \geq$} & \multicolumn{2}{c}{unWISE} &  \multicolumn{2}{c}{ALLWISE}   \\ 
                                             & \multicolumn{1}{c}{W1} & \multicolumn{1}{c}{W2} & \multicolumn{1}{c}{W3} & \multicolumn{1}{c}{W4}  \\ 
    \hline
    5.00   &   362 ( 78.2\%)   &   308 ( 66.5\%)  &    51 ( 11.0\%)  &    10 (  2.2\%) \\ 
    5.70   &   186 ( 69.4\%)   &   151 ( 56.3\%)  &    15 (  5.6\%)  &     2 (  0.7\%) \\ 
    6.00   &   109 ( 63.7\%)   &    91 ( 53.2\%)  &     8 (  4.7\%)  &     2 (  1.2\%) \\ 
    6.19   &    63 ( 72.4\%)   &    47 ( 54.0\%)  &     3 (  3.4\%)  &     2 (  2.3\%) \\ 
    6.50   &    34 ( 85.0\%)   &    26 ( 65.0\%)  &     1 (  2.5\%)  &     2 (  5.0\%) \\ 
    6.78   &    12 ( 85.7\%)   &     9 ( 64.3\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.00   &     4 (100.0\%)   &     4 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    7.50   &     1 (100.0\%)   &     1 (100.0\%)  &     0 (  0.0\%)  &     0 (  0.0\%) \\ 
    \hline \hline
  \end{tabular}
  \caption{Detection rates in the mid-infrared bands from WISE as a function of 
    redshift. A signal-to-noise cut of {\tt w$x$snr}$>3.0$ has been used for each band.}
  \label{tab:WFCAM_vs_VISTA}
\end{table}

@@

\begin{figure}
  %% trim=l b r t
  \includegraphics[width=8.6cm, clip, trim=2mm 0mm 2mm 0mm]
  {/cos_pc19a_npr/programs/quasars/highest_z/detections/WISEsnrW1W2W3W4_2by3_v1.pdf}
  \centering
  \vspace{-14pt}
  \caption[]{WISE signal-to-noise measures for the four bands, as well
    as for (W1-W2) colour.  The points are colour coded by redshift.}
  \label{fig:WISEmag_vs_coverage}
\end{figure}

@@

Recently, \citet{Assef2018} released two large catalogues of AGN 
candidates identified across 30,000 deg$^2$ of extragalactic sky 
from the WISE AllWISE Data Release. The ``R90'' catalogue, is 
contains 4.5M AGN candidates at 90\% reliability (and $\approx$150 
AGN candidates per deg$^2$) while the ``C75'' catalogue  
consists of 20.9M AGN candidates at 75\% completeness (and 
($\approx$700 AGN candidates per deg$^2$).  Crossmatching 
out catalogue of 463 VH$z$Qs with these catalogues, produces 
42 matches with	the R90 sample and 98 matches with the C75 sample. 
Both catalogues unsurprisingly match to the ultraluminous quasar 
SDSS J0100+2802 \citep{Wu2015} while the C75, but not the R90 catalogue 
matches to ULAS J1120+0641 \citep{Mortlock2011}. Neither catalogue 
matches J1342+0928 \citep{Banados2018}.

\begin{figure}
    \centering
    \includegraphics[width=8.6cm,  clip, trim=6mm 4mm 6mm 10mm]
    {../color_color/W1W2_plots/W1W2W3_hexplots_20190610v2.png} 
  \vspace{-14pt}
    \caption{The (W2-W3) vs. (W1-W2) colour – colour diagram showing the WISE colours 
      for the 283 VH$z$Q that have reported w3mpro values (blue to red coloured points).
      400,000 quasars at redshift $z\lesssim3.0$ from the DR14Q are also shown
      (grey colour-scale). }
    \label{fig:W1W2W3}
\end{figure}

\subsection{MIR Colours}
Figure~\ref{fig:W1W2W3} shows the (W1-W2) vs. (W2-W3) colour – colour
space diagram showing the WISE colours for the 283 VH$z$Q that have
reported w3mpro values (blue to red coloured points).  400,000 quasars
at redshift $z\lesssim3.0$ from the DR14Q are also shown (grey
colour-scale). 
%%
The VH$z$Q with the bluest colour in (W1 - W2) is 
DELS J1048-0109 with (W1-W2) = 0.154 
(see Figure~\ref{fig:DELS_J1048}).

@@

\begin{figure*}
    \centering
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/UHS_J0439+1634.png} 
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J0100+2802.png}
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1443+3623.png}
    \includegraphics[width=0.24\textwidth]{../data/WISE/image_thumbnails/SDSS_J1623+4705.png}
    \caption{ (a) UHS J0439+1634 
                 (b) SDSS J0100+280 
               (c) SDSS J1443+3623 
 (d) SDSS J1623+4705
}
    \label{fig:foobar}
\end{figure*}

@@

\subsection{Variability}
VH$z$Qs, if accreting at, or above the Eddington Limit, might well
have have large values of changing mass accretion rate, $\ddot{m}_{\rm
accr}$. A consequence of this would be that these quasar exhibit signs
of variability, most likely showing up in their UV/optical rest-frame
spectra. We look for evidence of this variability signature in the NIR
and MIR light-curves of the VH$z$Qs. As a guide, \civ enters the
$Y$-band at redshift $z$=5.32 and exits at $z$=5.99, and enters the
$J$-band at redshift $z=6.55$ and exits at $z$=7.57. \mgii enters the
$H$-band at redshift $z=4.33$ and exits at $z=5.37$ and enters the
$K$-band at redshift $z=6.25$ and exits at $7.50$.
